---
title: "Saving Plots"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


```{r setup}
library(ggEDA)
library(htmlwidgets) # install with `install.packages("htmlwidgets")`
library(ggplot2)
```

There are many ways to save ggEDA plots. Two convenient strategies are

1. Save interactive plots as self-contained HTML files using the `saveWidget()` function from `htmlwidgets`.
2. Save static plots as png/tiff/pdf/etc. using the `ggsave()` function from `ggplot2`

## Saving interactive plots to HTML

```{r,  fig.width = 7, fig.height = 5, eval=FALSE}

# Create an interactive plot
interactive_plot <- ggstack(
  baseballfans,
  col_id = "ID",
  col_sort = "Glasses",
  interactive = TRUE,
  verbose = FALSE,
  options = ggstack_options(legend_nrow = 2)
)

# Save as a self-encapsulated html widget
saveWidget(interactive_plot, file = "interactive_plot.html")
```

## Saving static plots

Simply create a non-interactive version of your plot and use ggsave.

```{r,  fig.width = 7, fig.height = 5, eval=FALSE}

# Create an static plot
myplot <- ggstack(
  baseballfans,
  col_id = "ID",
  col_sort = "Glasses",
  interactive = FALSE, # Turn interactivity off
  verbose = FALSE,
  options = ggstack_options(legend_nrow = 2)
)

# Save as png/tiff/pdf etc.
ggsave(filename = "my_plot.png", plot = myplot, width = 7, height = 5, dpi = 300) 
ggsave(filename = "my_plot.tiff", plot = myplot, width = 7, height = 5, dpi = 300) 
ggsave(filename = "my_plot.pdf", plot = myplot, width = 7, height = 5) 
```

For publication, you often want to set the `dpi` argument of `ggsave` to `300` for higher resolution images.
